### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsubsection{Cryptography Libraries}
The first side-channel attack of cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. Many algorithms (Diffie-Helloman, RSA) implementations at that time use the simple modular exponentiation algorithm, which does not run in fixed time. By measuring the time differences between the  modular exponentiation algorithm computes the exponent bits (0 or 1), an attacker can recover the whole secret key bit by bit. Many well-known cryptography algorithms are vulnerable to side-channels.

\subsubsection{Machine Learning and Deep Learning Models}
Previous side-channel attack mainly focus on recovering the input of the model and reversing the architecture of deep learning models. Hua et al.~\cite{hua2018reverse} were the first reverse engineer the architecture of neural networks. Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network based on the power consumption to recover the real-world inputs. For the MNIST dataset, their attacks can achieve up 89\% accuracy. On the contrary, our attack based on the page access information can achieve accuracy. CSI NN~\cite{batina2019csi} reverse engineer the multi-layer perception and convolution neural network based on the Electromagnetic signal. Cache Telepathy~\cite{yan2020cache} introduce the cache based side-channel attack to extract DNN architecture. We mention that all existing approach need a lot of domain knowledge and expertise to launch the attack.
\subsubsection{Media and Graphic Libraries}
A few of recent work also studies the side-channel in media and graphic libraries. In the first controlled-channel attack~\cite{xu2015controlled}, they can recover the outline of the image by exploiting the vulnerability in the inverse DCT leakage site. Daimeng et al.~\cite{wang2019unveiling} present the cache attack in graphic libraries. Their approaches also combine a machine learning approach. However, they use the machine learning to infer the best exploitable cache line, while our approach use the machine learning to infer the total leaked information.
\subsubsection{Others}
Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}. The attack to font libraries is essentially the same to the attack to the graphic library like GTK. By exploiting the differences of memory accesses when the program render each character, an attacker can recover part of the original sensitive information. We find most of those side-channel attacks target the trusted execution environments. We think part of the reason is that it is easy to argue that information in those libraries is also sensitive to users as well.

>>>>

\subsubsection{Cryptography Libraries}
The first side-channel attack of cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. Many algorithms (Diffie-Helloman, RSA) implementations at that time use the simple modular exponentiation algorithm, which does not run in fixed time. By measuring the time differences between the  modular exponentiation algorithm computes the exponent bits (0 or 1), an attacker can recover the whole secret key bit by bit. Cryptography libraries usually have several implementations for symmetric ciphers.
Symmetric ciphers like AES can have more than five implementations (OpenSSL). The reference implementation usually adopts T-Tables and S-Tables to speed up the computations. However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}. In addition to the reference implementation, those libraries also have side channel silent versions. However, recent studies also shows those versions also have side-channel vulnerabilities caused by compiler optimizations and human mistakes.
\subsubsection{Machine Learning and Deep Learning Models}
Previous side-channel attack mainly focus on recovering the input of the model and reversing the architecture of deep learning models. Hua et al.~\cite{hua2018reverse} were the first reverse engineer the architecture of neural networks. Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network based on the power consumption to recover the real-world inputs. For the MNIST dataset, their attacks can achieve up 89\% accuracy. On the contrary, our attack based on the page access information can achieve accuracy. CSI NN~\cite{batina2019csi} reverse engineer the multi-layer perception and convolution neural network based on the Electromagnetic signal. Cache Telepathy~\cite{yan2020cache} introduce the cache based side-channel attack to extract DNN architecture. We mention that all existing approach need a lot of domain knowledge and expertise to launch the attack.
\subsubsection{Media and Graphic Libraries}
A few of recent work also studies the side-channel in media and graphic libraries. In the first controlled-channel attack~\cite{xu2015controlled}, they can recover the outline of the image by exploiting the vulnerability in the inverse DCT leakage site. Daimeng et al.~\cite{wang2019unveiling} present the cache attack in graphic libraries. Their approaches also combine a machine learning approach. However, they use the machine learning to infer the best exploitable cache line, while our approach use the machine learning to infer the total leaked information.
\subsubsection{Others}
Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}. The attack to font libraries is essentially the same to the attack to the graphic library like GTK. By exploiting the differences of memory accesses when the program render each character, an attacker can recover part of the original sensitive information. We find most of those side-channel attacks target the trusted execution environments. We think part of the reason is that it is easy to argue that information in those libraries is also sensitive to users as well.
